HPC--101\\Onboarding

### 2016-08-30 hpc_101/paper.tex
author line
Removed names from cheatsheet, and modified the array view to look correct compared to slurm squeue output

\author{Gwen Jacobs Ph.D,\\Sean Cleveland Ph.D, Ron Merrill Ph.D,\\David Schanzenbach M.S.}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

@@

[login lus]\$ squeue
JOBID      PARTITION    NAME     USER    ST   TIME    NODES  NODELIST(REASON)
470[1-30]  community.q  example  user99  PD   00:00   1      (resource)
470_1      community.q  example  user99  R    00:01   1      compute-0001
470_2      community.q  example  user99  R    00:05   1      compute-0002
\end{semiverbatim}
\end{block}
\end{frame}

>>>>

\author{Gwen Jacobs Ph.D.,\\Sean Cleveland Ph.D., Ron Merrill Ph.D.,\\Jennifer Geis M.S., David Schanzenbach M.S.}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

@@

[login lus]\$ squeue
JOBID      PARTITION    NAME     USER    ST   TIME    NODES  NODELIST(REASON)
470[3-30]  community.q  example  user99  PD   00:00   1      (resource)
470_1      community.q  example  user99  R    00:01   1      compute-0001
470_2      community.q  example  user99  R    00:05   1      compute-0002
\end{semiverbatim}
\end{block}
\end{frame}
